Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-08-20 surfaces-write-up/surface-write-up.tex
reference Te definition in hirzebruch statement

\begin{restatable}{thm}{hirzrestate}
\label{thm:hirz-generators-relations}
Let $D = \sum_{i = 1}^n \alpha_i D_i \in \bq
\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i}$.
Write $\ell_{i,j} := \lcm_{h\ne i,j}(k_h)$.
Let $u, v, z, w$ be the coordinates for the Hirzebruch surface
$\hirz_m$, as described at the beginning of Section
~\ref{sec:hirz}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
Now suppose that $\{f_1, \ldots, f_n\}$ contains two independent 
linear polynomials in $u, v$ and two independent linear polynomials in
$w, x$ {\rm(}with corresponding $\alpha_j$ possibly zero{\rm)}.

@@

\begin{defn}
Define 
\begin{equation*}
	\Te(D) = \left\{i \in \{1, \ldots, n\}: \bida_i \sum_{k=1}^n \bidb_k 
\alpha_k = \bidb_i \sum_{k=1}^n \bida_k \alpha_k \right\},
\end{equation*}

>>>>

\begin{restatable}{thm}{hirzrestate}
\label{thm:hirz-generators-relations}
Let $D = \sum_{i = 1}^n \alpha_i D_i \in \bq
\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i}$.
Write $\ell_{i,j} := \lcm_{h\ne i,j}(k_h)$.
Let $u, v, z, w$ be the coordinates for the Hirzebruch surface
$\hirz_m$, as described at the beginning of Section
~\ref{sec:hirz} and define $\Te, \Tp, \Tm$ as in Definition ~\ref{defn:t-defn}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
Now suppose that $\{f_1, \ldots, f_n\}$ contains two independent 
linear polynomials in $u, v$ and two independent linear polynomials in
$w, x$ {\rm(}with corresponding $\alpha_j$ possibly zero{\rm)}.

@@

\begin{defn}
\label{defn:t-defn}
Define 
\begin{equation*}
	\Te(D) = \left\{i \in \{1, \ldots, n\}: \bida_i \sum_{k=1}^n \bidb_k 
\alpha_k = \bidb_i \sum_{k=1}^n \bida_k \alpha_k \right\},
\end{equation*}
